Missing links and the topological robustness of food webs

### 2023-02-10 manuscript/ms_C3_v3.tex
updated ms

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, with potential consequences for the perceived functioning
  and stability of the food webs. Undersampling can be compensated for
  by using food web models such as the allometric diet breadth model
  (ADBM) to predict missing links. Simultaneously, models might predict
  links which cannot occur, i.e., false positives.
\item
  Previous research shows that (i) food web robustness (the inverse of
  the number of secondary extinctions occurring due to primary
  extinctions) increases with connectance (the number of realised
  trophic links divided by the number of possible links), and (ii) that
  model predicted food webs usually have greater connectance than
  observed ones. Thus, we expect that predicted food webs are more
  robust than observed ones. However, this expectation has never, to our
  knowledge, been tested, nor has the effect size, i.e.~the difference
  in robustness of predicted and observed food web with respect to the
  difference in their connectance, been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links but does not predict all links
  correctly. We did this for 12 different food webs from a wide variety
  of ecosystems. We used three extinction scenarios: random, most
  connected, and least connected.
\item
  We found, as expected, that the predicted food webs were more robust
  than the observed food webs, which can be attributed to the higher
  connectance of the predicted food webs. On average, for every one unit
  of increase in connectance, we found that the food webs robustness
  increased by 0.52 units for the most connected species extinction
  scenario and by 0.04 units for the random species extinction
  scenarios. On the other hand, we saw no effect, on average, of
  increased connectance for the least connected species extinction
  scenario for all except two of the 12 food webs.
\item
  These results show that undersampling can lead to large underestimates
  of food web robustness that can be compensated for by filling in
  missing links with food web models. Nevertheless, increased
  connectance may contribute to lower dynamical stability, so it would
  be interesting to compare the dynamical stability of observed and
  predicted food webs and the topological stability that we have focused
  on.
\end{enumerate}
\end{abstract}

@@

@@

A key assumption of the observed food webs is that they are very well
sampled, i.e.~all the links that in reality can occur are represented.
However, it is known that not all food webs are very well sampled and do
not represent all of the feeding links that can occur (Caron et al.,
2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
require more sampling effort than others, whereas some trophic links
remain unobserved because of biological constraints such as
spatio-temporal uncoupling, size or reward mismatching, foraging
constraints and physiological-biochemical constraints, which are
irrespective of sufficient sampling effort (Jordano, 2016). Previous
studies such as Caron et al. (2022) and Gupta et al. (2022) have shown
that the predicted food webs from these models usually have greater
connectance than the observed ones. One solution to compensate for
undersampling is using a food web model such as the Allometric Diet
Breadth Model (ADBM) (Petchey et al., 2008) to predict the missing links
and then measure the robustness of the predicted food web. The ADBM is a
mechanistic model constructed using foraging rules based on the body
sizes of prey and predator, where trophic interactions satisfying those
rules would be predicted by the model, which are perhaps not observed
because those interactions are rare. However, this solution is not
infallible, as it is likely that the food web model might still miss
some links and also may predict some links that could not, in fact
occur.

In our study, we investigate the topological robustness of the ADBM
predicted food webs and compare it to that of the observed food webs. We
expect the ADBM predicted food webs to be more robust than the observed
food webs, and for the greater robustness to be related to the amount by
which the ADBM predicts greater connectance compared to that of the
observed food webs. We do this by simulating primary species loss in 12
food webs predicted by the ADBM to quantify the secondary loss of
extinctions and compare the robustness of food webs predicted by the
ADBM to the robustness of the observed food webs. We use three different
approaches of primary species removal: (i) most connected species, (ii)
random species and (iii) least connected species to understand if the
outcome varies among these approaches.

@@

@@

We first present the secondary extinction curves of the ADBM predicted
food webs which had the maximum true skill statistics and of the
observed food webs for 12 food webs under three different extinction
scenarios. We then compare the robustness of all the ADBM predicted food
webs within the 95\% prediction interval against that of the observed
food webs to take into account uncertainty in the robustness across food
webs predictions. Finally, we quantify the effect of the difference in
their connectance on the difference in their robustness estimates.

\hypertarget{secondary-extinctions}{%
\subsection{Secondary extinctions}\label{secondary-extinctions}}

In the most connected extinction scenario, the cumulative secondary
extinction curves started to rise steeply in the observed food webs at a
lower number of primary species removal as compared to the ADBM
predicted food webs for nine food webs (Fig. \ref{fig:fig_r1} (a, c, d,
e, f, g, h, j, l)). However, there was a higher number of cumulative
secondary extinctions occurring in the ADBM predicted food webs when
compared to that of the observed food webs at a high number of primary
species removal in five food webs (Fig. \ref{fig:fig_r1} (a, f, g, h,
k)). In the Skipwith Pond food web, there were no secondary extinctions
for any number of primary removal of species (Fig. \ref{fig:fig_r1}
(i)), whereas in the Broadstone Stream (taxonomic aggregation) food web
the same was true only for the observed food web but in the ADBM
predicted food web there was a steep rise in the cumulative secondary
extinctions (Fig. \ref{fig:fig_r1} (b)).

{\centering \includegraphics[width=400px]{../results/plot_mostconnected_maxTSS}

\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-2}
\end{figure}

In Fig. \ref{fig:fig_r2}, we present the cumulative secondary
extinctions in the ADBM predicted and the observed food webs for five
(out of 1000) independent random extinction sequences to show example
variation caused by different random primary extinction orders. The
secondary extinction curves of the ADBM predicted food webs were steeper
than that of the observed food webs, i.e.~primary removal of some
species in an extinction sequence can lead to the complete collapse of
the remaining food web in the ADBM predicted food webs.

{\centering \includegraphics[width=400px]{../results/plot_ra_extlines_maxTSS}

\caption{\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-3}
\end{figure}

Compared to the most connected and random extinction scenarios, there
were fewer secondary extinctions in the least connected extinction
scenario, and therefore the secondary extinction curves were flat for
many of the food webs (Fig. \ref{fig:fig_r3}). In some of the food webs,
the extinction curves of the ADBM predicted food webs overlapped with
the observed food webs (Fig. \ref{fig:fig_r3} (b, c, g, h, i, k, l)\}).
In five of the food webs, a very high number of secondary extinctions
occurred at a very low number of primary species removal (Fig.
\ref{fig:fig_r3} (a, d, e, f, j)).

{\centering \includegraphics[width=400px]{../results/plot_leastconnected_maxTSS}

\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the \textbf{least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-4}
\end{figure}

\hypertarget{robustness}{%
\subsection{Robustness}\label{robustness}}

The ADBM predicted food webs were more robust than the observed food
webs on average in the most connected and random extinction scenarios
(Fig. \ref{fig:fig_r4} (a, b)). However, there were large variations in
the robustness within the ADBM predicted food webs in the most connected
extinction scenario (Fig. \ref{fig:fig_r4} (a)). For example, the ADBM
predicted Caricaie Lakes food web was more robust than the observed food
web on average but had a larger variation in the robustness within the
ADBM predicted food webs compared to other food webs.

The food webs were more robust to the random extinction scenario than
the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
and Benguela Pelagic food webs had more variations in robustness within
the ADBM predicted food webs as compared to the other food webs (Fig.
\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
aggregation) and Broadstone Stream (size aggregation) food webs were the
most robust (Median \(R_{50} = 0.5\)) for both ADBM predicted and
observed food webs. Although there were few less robust ADBM predicted
food webs in the Broadstone Stream (size aggregation) as shown by the
outliers. The food webs were more robust to the random extinction
scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a,
b)). Small Reef and Benguela Pelagic food webs had more variations in
robustness within the ADBM predicted food webs as compared to the other
food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream
(taxonomic aggregation) and Broadstone Stream (size aggregation) food
webs were the most robust (Median \(R_{50} = 0.5\)) for both ADBM
predicted and observed food webs. Although there were few less robust
ADBM predicted food webs in the Broadstone Stream (size aggregation) as
shown by the outliers.

In the least connected extinction scenario, the food webs had a very
high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
(Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The
ADBM predicted food webs for Small Reef and Benguela Pelagic had very
low median robustness. Benguela Pelagic, Broom and Capinteria food webs
from the ADBM had larger variations in robustness when compared to that
of the others.

@@

\caption{\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. Some points are not visible due to perfect overlap in b and c. Refer to Fig. 7 in the Supplementary Information for a faceted visualisation. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
\end{figure}

In all of the food webs except Small Reef and Broadstone Stream
(taxonomic aggregation), the effect size of connectance on robustness
was positive on average in the most connected extinction scenario (Fig.
\ref{fig:fig_r5} (a)), i.e.~greater connectance had a positive effect on
the robustness. In the random extinction scenario, there was a positive
effect of greater connectance on the robustness for Ythan, Small Reef,
Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela
Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied
across the food webs. In the least connected extinction scenario, the
median effect sizes were zero or very close to zero for all the food
webs except Benguela Pelagic and Small Reef food webs where the median
effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
were lots of outlier effect sizes less than zero.

@@

\caption{\label{fig:fig_r5} Effect size (i.e. ratio of the difference in normalised robustness between ADBM predicted food webs and observed food webs to the difference in their normalised connectance) shown for the 12 food webs. Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-6}
\end{figure}

@@

As expected, the ADBM predicted food webs were more robust than the
observed food webs on average. The considerable variation of the
robustness of the ADBM predicted food webs suggests, however, that
undersampling in food webs can lead to considerable uncertainty in the
estimates of food web robustness, even when a model is used to
compensate for undersampling. Furthermore, as was previously found, the
food webs are least robust to primary extinction of the most connected
species compared to that of least connected and random extinction
scenarios on average. Future development would be to understand how
undersampling, i.e.~predicted greater connectance, influences the
stability of the dynamics of the ADBM predicted food webs against that
of the observed food webs and compare it with the patterns in our study
in which extinction occur only by topological criteria. However, one
would expect a decrease in food web stability with greater connectance
(Martinez et al., 2006; May, 1972).

@@

@@

As with any food web model, we expect that there are real false
positives in the food webs predicted by the ADBM. Real false positive
means that the food web model predicts a link between two species that
can never interact. (The other type of false positive is when the model
predicts a link that was not observed but could have been observed if
the food web was sampled enough. In this case, further sampling should
result in the link being observed and a change from false positive to
true positive.) Firstly, this may be because the ADBM uses only body
size as a trait. A trait uncorrelated with the body size may be
influential in determining the interaction between two species (Gupta et
al., 2022). Secondly, the ADBM can only predict diets that are
contiguous with respect to the size of the prey. I.e. it cannot predict
that the consumer will consume prey of size 1 and 3, and not consume
prey of size 2. However, it is important to note that observed diets are
not always contiguous when prey are ordered by their size due to some
ecological differences in how predator species choose their prey (Caron
et al., 2022). Hence, it would be intriguing to extend our study to use
other food web models based on size-based rules, such as Gravel et al.
(2013) and Vagnon et al. (2021), to understand if the results are
dependent on the decision of model selection. We expect to get a similar
result in a size-based deterministic model but a different result,
i.e.~lower robustness in a size-based stochastic model as compared to
the ADBM because the latter can take into account non-contiguity in
predator diets (Williams et al., 2010). It would also be interesting to
use food web models not based on body size, such as Cattin et al. (2004)
and Allesina et al. (2008). We expect to have a difference in results
based on whether the trophic interactions in the food webs are governed
by size-structured rules or not.

@@

\caption{\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs. Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-8}
\end{figure}

@@

>>>>

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, with potential consequences for the perceived functioning
  and stability of the food webs. Undersampling can be compensated for
  by using food web models such as the allometric diet breadth model
  (ADBM) to predict missing links. Simultaneously, models might predict
  links which cannot occur, i.e., real false positives.
\item
  Previous research shows that (i) food web robustness (the inverse of
  the number of secondary extinctions occurring due to primary
  extinctions) increases with connectance (the number of realised
  trophic links divided by the number of possible links), and (ii) that
  model predicted food webs usually have greater connectance than
  observed ones. Thus, we expect that predicted food webs are more
  robust than the observed ones. However, this expectation has never, to
  our knowledge, been tested, nor has the effect size, i.e.~the
  difference in robustness of predicted and observed food web with
  respect to the difference in their connectance, been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links. We did this for 12 different food
  webs from a wide variety of ecosystems. We used three extinction
  scenarios: random, most connected, and least connected.
\item
  We found, as expected, that the predicted food webs were more robust
  than the observed food webs, which can be attributed to the higher
  connectance of the predicted food webs. On average, for every one unit
  of increase in connectance, we found that the food webs robustness
  increased by 0.52 units for the most connected species extinction
  scenario and by 0.04 units for the random species extinction
  scenarios. On the other hand, we saw no effect or very little effect,
  on average, of increased connectance for the least connected species
  extinction scenario for all except two of the 12 food webs.
\item
  These results show that undersampling can lead to large underestimates
  of food web robustness that can be compensated for by filling in
  missing links with food web models. Also, the differences in the
  structural properties of the model predicted food webs and the
  observed food webs suggest structural properties of a food web could
  be used as summary statistics to fit models such as the ADBM to the
  observed data.
\end{enumerate}
\end{abstract}

@@

\hypertarget{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}{%
\subsection{Paragraph on how other structural food web properties are
responsible as
well}\label{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}}

Structural properties other than food web connectance such as the
proportion of basal species and the maximum trophic level of species in
a food web can influence the robustness of a food web (Mendonça et al.,
2022; Riede et al., 2011). For example, a food web with a higher
proportion of basal species on average will be more robust as compared
to otherwise (Mendonça et al., 2022) because extinctions of all the
basal species will lead to collapse of the complete food web. A food web
with a lower maximum trophic level of species on average will be more
robust as compared to otherwise (Riede et al., 2011). This is because a
food web with a lower maximum trophic level will have higher number of
species per trophic level on average as compared to otherwise.

@@

A key assumption of the observed food webs is that they are very well
sampled, i.e.~all the links that in reality can occur are represented.
However, it is known that not all food webs are very well sampled and do
not represent all of the feeding links that can occur (Caron et al.,
2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
require more sampling effort than others, whereas some trophic links
(sometimes referred to as forbidden links) remain unobserved because of
biological constraints such as spatio-temporal uncoupling, size or
reward mismatching, foraging constraints and physiological-biochemical
constraints, which are irrespective of sufficient sampling effort
(Jordano, 2016). Previous studies such as Caron et al. (2022) and Gupta
et al. (2022) have shown that the predicted food webs from these models
usually have greater connectance than the observed ones. One solution to
compensate for undersampling is using a food web model such as the
Allometric Diet Breadth Model (ADBM) (Petchey et al., 2008) (reference
(gut content paper)) to predict the missing links and then measure the
robustness of the predicted food web. The ADBM is a mechanistic model
constructed using foraging rules based on the body sizes of prey and
predator, where trophic interactions satisfying those rules would be
predicted by the model, which are perhaps not observed because those
interactions are rare. However, this solution is not infallible, as it
is likely that the food web model might still miss some links and also
may predict some links that could not, in fact occur.

In our study, we investigate the topological robustness of the ADBM
predicted food webs and compare it to that of the observed food webs. We
achieved this by simulating primary species loss in 12 food webs
predicted by the model to quantify secondary loss of extinctions and
compare the robustness of food webs predicted by the model to the
robustness of the observed food webs. We expect the model predicted food
webs to be more robust than the observed food webs, and for the greater
robustness to be related to the amount by which the model predicts
greater connectance compared to that of the observed food webs. We also
examined how different structural food web properties other than the
connectance can influence this difference in the perceived robustness.
In order to do that, we define our null hypothesis to be: (H1) The
missing links that are filled in by the model increase robustness
because they increase connectance; and our alternate hypothesis to be:
(H2) Although the model fills in missing links, it also changes other
structural properties and these outweigh the effects of connectance on
robustness.

@@

All food webs with one exception (Broadstone Stream) was available only
at the species level, i.e.~with information about interactions between
species and the body size of species. We use the term ``species'' in
this study to indicate a ``node'' in a food web in which nodes are
connected by trophic interactions, and nodes are a collection of
individuals that share links. These species/nodes are not always
taxonomic species, but can be broader taxonomic ranks.

In contrast, the Broadstone Stream food web data contained interactions
between individuals and the individual body sizes. Thus, the Broadstone
Stream food web can be constructed by aggregating by either taxonomy or
size (Woodward et al., 2010).

@@

We first compare the robustness of the model food webs against that of
the observed food webs. We then quantify the effect of difference in
their connectance on the difference in their robustness estimates.

The model food webs were more robust than the observed food webs on
average in the most connected and random extinction scenarios (Fig.
\ref{fig:fig_r4} (a, b)). However, there were large variations in the
robustness within the model food webs in the most connected extinction
scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs
for the Caricaie Lakes food web was more robust than the observed food
web on average but had a larger variation in the robustness within the
model food webs compared to other food webs.

The food webs were more robust to the random extinction scenario than
the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
and Benguela Pelagic food webs had more variations in robustness within
the model food webs as compared to the other food webs (Fig.
\ref{fig:fig_r4} (b)). Skipwith Pond and Broadstone Stream (taxonomic
aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
for both model and observed food webs. The food webs were more robust to
the random extinction scenario than the most connected scenario (Fig.
\ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had
more variations in robustness within the model food webs as compared to
the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond,
Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size
aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
for both model and observed food webs. Although there were few less
robust model food webs in the Broadstone Stream (size aggregation) as
shown by the outliers.

In the least connected extinction scenario, the food webs had a very
high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
(Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The
model food webs for Small Reef and Benguela Pelagic had very low median
robustness. The model food webs for the Benguela Pelagic, Broom and
Capinteria food webs had larger variations in robustness when compared
to that of the others.

@@

\caption{\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. Some points are not visible due to perfect overlap in b and c. Refer to Fig. 7 in the Supplementary Information for a faceted visualisation. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-2}
\end{figure}

In all of the food webs except Broadstone Stream (taxonomic aggregation)
and Skipwith Pond, the effect size of connectance on robustness was
positive on average in the most connected extinction scenario (Fig.
\ref{fig:fig_r5} (a)), i.e.~greater connectance had a positive effect on
the robustness. In the random extinction scenario, there was a positive
effect of greater connectance on the robustness for Ythan, Small Reef,
Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela
Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied
across the food webs. In the least connected extinction scenario, the
median effect sizes were zero for all the food webs except for Caricaie
Lakes and Capinteria food webs where the effect sizes were very close to
zero and for Benguela Pelagic and Small Reef food webs where the median
effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
were lots of outlier with effect sizes negative.

@@

\caption{\label{fig:fig_r5} Effect size (i.e. ratio of the difference in normalised robustness between ADBM predicted food webs and observed food webs to the difference in their normalised connectance) shown for the 12 food webs. Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

As expected, the model food webs were more robust than the observed food
webs on average. The considerable variation of the robustness of the
model food webs suggests, however, that undersampling in food webs can
lead to considerable uncertainty in the estimates of food web
robustness, even when a model is used to compensate for undersampling.
Furthermore, as was previously found, the food webs are least robust to
primary extinction of the most connected species compared to that of
least connected and random extinction scenarios on average. Future
development would be to understand how undersampling, i.e.~predicted
greater connectance, influences the stability of the dynamics of the
model food webs against that of the observed food webs and compare it
with the patterns in our study in which extinction occur only by
topological criteria. However, one would expect a decrease in food web
stability with greater connectance (Martinez et al., 2006; May, 1972).

@@

\hypertarget{a-paragraph-on-the-implication-of-our-study}{%
\subsection{A paragraph on the implication of our
study}\label{a-paragraph-on-the-implication-of-our-study}}

\begin{itemize}
\tightlist
\item
  On the uncertainty in the ADBM estimates
\item
  On the limitation of a food web model
\item
  On undersampling
\end{itemize}

Our study also depicts that the uncertainty in the model predictions can
have a strong influence on the perceived robustness of the observed food
webs. The large variations in the robustness of the observed food webs
suggest why it is crucial to incorporate uncertainty in the food web
predictions. At the same time, our study also quantifies the impact of
undersampling on the perceived robustness of the observed food webs and
thus influencing the perceived functioning and stability of the food
webs (reference). This strongly suggest why it is crucial to incorporate
the influence of undersampling.

@@

As with any food web model, we expect that there are real false
positives in the food webs predicted by the ADBM. Real false positive
means that the food web model predicts a link between two species that
can never interact (The other type of false positive is when the model
predicts a link that was not observed but could have been observed if
the food web was sampled enough. In this case, further sampling should
result in the link being observed and a change from false positive to
true positive.). Firstly, this may be because the ADBM uses only body
size as a trait. A trait uncorrelated with the body size may be
influential in determining the interaction between two species (Gupta et
al., 2022). Secondly, the ADBM can only predict diets that are
contiguous with respect to the size of the prey. I.e. it cannot predict
that the consumer will consume prey of size 1 and 3, and not consume
prey of size 2. However, it is important to note that observed diets are
not always contiguous when prey are ordered by their size due to some
ecological differences in how predator species choose their prey (Caron
et al., 2022). Hence, it would be intriguing to extend our study to use
other food web models based on size-based rules, such as Gravel et al.
(2013) and Vagnon et al. (2021), to understand if the results are
dependent on the decision of model selection. We expect to get a similar
result in a size-based deterministic model but a different result,
i.e.~lower robustness in a size-based stochastic model as compared to
the ADBM because the latter can take into account non-contiguity in
predator diets (Williams et al., 2010). It would also be interesting to
use food web models not based on body size, such as Cattin et al. (2004)
and Allesina et al. (2008). We expect to have a difference in results
based on whether the trophic interactions in the food webs are governed
by size-structured rules or not.

@@

\caption{\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs. Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions). Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5. The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\leavevmode\vadjust pre{\hypertarget{ref-woodwardChapterIndividualBasedFood2010}{}}%
Woodward, G., Blanchard, J., Lauridsen, R. B., Edwards, F. K., Jones, J.
I., Figueroa, D., Warren, P. H., \& Petchey, O. L. (2010). Chapter 6 -
{Individual-Based Food Webs}: {Species Identity}, {Body Size} and
{Sampling Effects}. In G. Woodward (Ed.), \emph{Advances in {Ecological
Research}} (Vol. 43, pp. 211--266). {Academic Press}.
\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}
